---
title: "Heart disease"
author: "Argen Almazbek uulu"
date: "April 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Context
This database contains 76 attributes, but all published experiments refer to using a subset of 14 of them. In particular, the Cleveland database is the only one that has been used by ML researchers to this date. The "goal" field refers to the presence of heart disease in the patient. It is integer valued from 0 (no presence) to 4.

Content

Attribute Information: 
1. age 
2. sex 
3. chest pain type (4 values) 
4. resting blood pressure 
5. serum cholestoral in mg/dl 
6. fasting blood sugar > 120 mg/dl
7. resting electrocardiographic results (values 0,1,2)
8. maximum heart rate achieved 
9. exercise induced angina 
10. oldpeak = ST depression induced by exercise relative to rest 
11. the slope of the peak exercise ST segment 
12. number of major vessels (0-3) colored by flourosopy 
13. thal: 3 = normal; 6 = fixed defect; 7 = reversable defect

The names and social security numbers of the patients were recently removed from the database, replaced with dummy values. One file has been "processed", that one containing the Cleveland database. All four unprocessed files also exist in this directory.

To see Test Costs (donated by Peter Turney), please see the folder "Costs"

Acknowledgements
Creators: 
1. Hungarian Institute of Cardiology. Budapest: Andras Janosi, M.D. 
2. University Hospital, Zurich, Switzerland: William Steinbrunn, M.D. 
3. University Hospital, Basel, Switzerland: Matthias Pfisterer, M.D. 
4. V.A. Medical Center, Long Beach and Cleveland Clinic Foundation: Robert Detrano, M.D., Ph.D.

Donor: David W. Aha (aha '@' ics.uci.edu) (714) 856-8779

Inspiration
Experiments with the Cleveland database have concentrated on simply attempting to distinguish presence (values 1,2,3,4) from absence (value 0).

See if you can find any other trends in heart data to predict certain cardiovascular events or find any clear indications of heart health.


```{r libs, message=F, warning=F}
library(dplyr)
library(ggplot2)
library(tidyr)
library(caret)
library(corrplot)
```

```{r data}
data <- read.csv('heart.csv', stringsAsFactors = F, encoding = 'UTF-8')
str(data)
colnames(data)[1] <- 'age'
str(data)
```

```{r EDA}
##Let's check for the missing values
sapply(data, function(X) sum(is.na(X)))

##Let's get the intuition of how many males and females are there in a dataset
ggplot(data, aes(x = factor(x = sex))) + geom_bar(fill ='blue')

## Here is the numbers of males and females (females = 0, males = 1)
data %>%
  group_by(sex) %>%
  summarize(n())

## Now let's see the distribution of Chest Pain Type variable
ggplot(data, aes(x = factor(cp))) + geom_bar(fill = 'blue')

## Age to target
data$age[data$age == 29] <- 31
AgeBins <- paste(seq(30,80,10),"'d")
data$age.B <- cut(data$age, seq(30,90,10),labels = AgeBins)
table(data$age.B, useNA = "always")
ggplot(data=data, aes(x=age.B,fill=factor(target))) + geom_bar()

## Resting blood preasure
summary(data$trestbps)
summary(data$age)
summary(data$chol)

ggplot(data, aes(x = 1, y = trestbps)) + geom_boxplot()
ggplot(data, aes(x = 1, y = chol)) + geom_boxplot()
  
```

#Feature Transformation
```{r transform}
ifelse(data$sex==0, 'female', 'male' )
data$sex <- as.factor(data$sex)
colnames(data)[3] <- 'chest_pain_type'
colnames(data)[4] <-'resting_blood_preasure'
colnames(data)[6] <- 'fasting_blood_sugar'
colnames(data)[8] <- 'max_heart_rate'
colnames(data)[9] <- 'excercise_induced_angina'
colnames(data)[13] <- 'thalassemia'
data$chest_pain_type <- as.factor(data$chest_pain_type)
data$fasting_blood_sugar <- as.factor(data$fasting_blood_sugar)
data$restecg <- as.factor(data$restecg)

```

#First Logistic Regression
```{r Linear Model}
data$target <- as.factor(data$target)
set.seed(1997)

features <- data %>% select(target, age.B, chest_pain_type, sex, resting_blood_preasure, chol, fasting_blood_sugar, restecg, max_heart_rate, thalassemia, excercise_induced_angina, oldpeak, slope, ca)
str(features)
sample_size <- floor(0.75*nrow(features))
sample_size
data_ind <- sample(seq_len(nrow(features)), size = sample_size)
head(data_ind, n=10)
data_sample <- features[data_ind,]
data_val <- features[-data_ind,]
labels_val <- data_val$target
data_val$target <- NULL



reg <- glm(target ~ ., data = features, family = binomial())
summary(reg)


preds <- predict(reg, newdata = data_val, type = "response")

confusionMatrix(as.factor(as.numeric(preds > 0.5)), labels_val)
head(data_val$target)
head(as.numeric(preds > 0.5))
```

#Correlation matrix
```{r Cor}
correlations <- cor(data[,c(1,5,4,8)])
correlations
corrplot(correlations)
```

#Second Regression
```{r Linear Model 2}
features2 <- data %>% select(target, chest_pain_type, sex, resting_blood_preasure, max_heart_rate, thalassemia, excercise_induced_angina, oldpeak, ca)
reg <- glm(target ~ ., data = features2, family = binomial())
summary(reg)


preds2 <- predict(reg, newdata = data_val, type = "response")

confusionMatrix(as.factor(as.numeric(preds2 > 0.5)), labels_val)
```